The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-02-12 paper/ms.tex
escape graction table

@@

In this case the $\mu$ distribution is not homogeneous as shown in
Figure \ref{fig:muhisto}. The off-center emision shows a variation at
the level of $20\%$ in intensity with the angle $\Theta$. {\bf Como se
ven los plots de otras velocidades y tau? Tambien son variaciones del
20\%?}. This variation implies that that the line is more intense in
the plane perpendicular to the rotation axis.

>>>>

\begin{table}
\begin{center}
\begin{tabular}{c c}
\hline \hline
Model, $\tau_{H}$ & $\ V_{max}(km\ s^{-1})$ $0, 50, 100, 200, 300$ \\
\hline \hline
Homogeneous $10^{5}$& $0.2637, 0.2661, 0.3091, 0.3570, 0.3709$ \\
Homogeneous $10^{6}$ & $0.2894, 0.2891, 0.3096, 0.3607, 0.3937$ \\
Homogeneous $10^{7}$ &$ 0.2279, 0.2298, 0.2318, 0.2547, 0.2813 $\\
Central $10^{5}$ & $0.0966, 0.0966, 0.0965, 0.0965, 0.0965$ \\
Central $10^{6}$ & $0.0663, 0.665, 0.0665, 0.0665, 0.665$ \\
Central $10^{7}$ & $0.0149, 0.0158, 0.0158, 0.0158, 0.0158$ \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

In this case the $\mu$ distribution is not homogeneous as shown in
Figure \ref{fig:muhisto}. The off-center emision shows a variation of flux at
the levels of $10\% - 28\%$ in intensity with the angle $\Theta$. In general 
models with a larger $\tau_{H}$ present a higher variation in the flux.
This variation implies that that the line is more intense in
the plane perpendicular to the rotation axis.
